Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications

### 2025-08-21 Submission.Rmd
avoiding conflict - stashing desktop and accepting these laptop revisions

Participants were first asked to think about whether or not their job could be described as consisting of these job characteristics. If a respondent indicated that any one characteristic was not applicable for their job (e.g., answered *never* or *not at all*), they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment). All questions were administered in randomized order within blocks of characteristic, resource, challenge, and hindrance.

@@

```{r overallhist, fig.cap="Frequency distribution of standard deviations across characteristics deemed resources, challenges, and demands."}

@@

H1 posits that the same job characteristic is not necessarily experienced similarly across workers - as hindrance, challenge, or resource. We explore this hypothesis first at the job characteristic level before presenting a broader perspective. Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] Figure \@ref(fig:combinegraphs) presents the resources, challenges, and hindrances that are *most consistently agreed on* as indexed by lowest empirical standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers. The figures demonstrate that what is perceived as resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`). However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).

@@

In addition to highlighting extremely agreed-- or disagreed--upon characteristics, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items. Here, discrepancies receive greater context, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram). Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to *hindrances*, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01). In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are differently experienced across our raters.

The second hypothesis, similarly oriented to H1, stated that job characteristics would not be *uniquely* categorized as a resource or demand. Table 1 provides the correlations among the O\*NET "scale"--level groupings^[Survey items are grouped by O\*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc). These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.] across evaluations as resource, challenge, and hindrance. Here would expect trivial correlations if job characteristics *were* uniquely categorized. First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16). Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.

The mean resource to challenge correlations within the same dimension ranged from .62 to .66 (*M* = .64, *SD* = .02; for example, the association between information input ratings as a resource and as a challenge was .62). The correlations between resources and challenges *across* dimensions (for example, the correlation between mental processes and work output was .42 and .39) ranged from .08 to .50, *M* = .32, *SD* = .12. The resource-hindrance correlations within the same dimension ranged from -.16 to -.30 (*M* = -.24, *SD* = .05), while the correlations between resources and hindrances *across* dimensions ranged from .05 to -.27, *M* = -.14, *SD* = .08. The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27 (*M* = -.21, *SD* = .08). The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, *M* = -.11, *SD* = .09.  In summary, correlations were larger when what was being rated was the same type of characteristic. Challenge and hindrance demands demonstrated smaller relationships, but mostly negative. Challenges and resources within the same O\*NET dimensions are strongly and positively related. These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a *resource* being also perceived as a *challenge*. Stated differently, job characteristics should not be uniquely categorized as resource or demand.

>>>>

Participants were first asked to think about whether or not their job could be described as consisting of these job characteristics. If a respondent indicated that any one characteristic was not applicable for their job (e.g., answered *never* or *not at all*), they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment). These ratings were made along a 5--point Likert--type agreement scale with values of (1) Strongly Disagree, (2) Disagree, (3) Neither Agree nor Disagree, (4) Agree, and (5) Strongly Agree. All questions were administered in randomized order within blocks of characteristic, resource, challenge, and hindrance.

@@

```{r overallhist, fig.cap="Frequency distributions of standard deviations across characteristics rated as resources, challenges, and demands."}

@@

H1 posits that *not everyone agrees* that a characterisitic is a hindrance, challenge, or resource. Figure \@ref(fig:overallhist) presents standard deviations of characteristic rating across all rated items. Here,the *spread* of difference exhibits wider distributions of (dis)agreement for challenge and resource ratings (and a relatively more leptokurtic distribution of (dis)agreement for hindrances). The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to *hindrances*, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01).

Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] Figure \@ref(fig:combinegraphs) presents the *most consistently agreed on* resources, hindrances, and challenges as indexed by lowest empirical standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers. The figures again highlight that what is perceived as resource and challenge tends to be relatively agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`). However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`). In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are differently experienced across our raters.

@@

The second hypothesis, similarly oriented to H1, stated that job characteristics would not be *uniquely* categorized as a resource or demand. We explore this via pattern of correlation similar in intent to @campbell1959convergent's multi--trait multi--method matrix. Table 1 provides the correlations among the O\*NET "scale"--level groupings^[Survey items are grouped by O\*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc). These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.] across evaluations as resource, challenge, and hindrance. Here would expect trivial correlations if job characteristics *were* uniquely categorized. First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16). Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.

The mean resource to challenge correlations within the same dimension ranged from .62 to .66 (*M* = .64, *SD* = .02; for example, the association between information input ratings as a resource and as a challenge was .62). The correlations between resources and challenges *across* dimensions (for example, the correlation between mental processes [resource] and work output [challenge] was .39) ranged from .08 to .50, *M* = .32, *SD* = .12. The resource-hindrance correlations within the same dimension ranged from -.16 to -.30 (*M* = -.24, *SD* = .05), while the correlations between resources and hindrances *across* dimensions ranged from .05 to -.27, *M* = -.14, *SD* = .08. The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27 (*M* = -.21, *SD* = .08). The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, *M* = -.11, *SD* = .09.  In summary, correlations were larger when what was being rated was the same type of characteristic. Challenge and hindrance demands demonstrated smaller relationships, but mostly negative. Challenges and resources within the same O\*NET dimensions are strongly and positively related. These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a *resource* being also perceived as a *challenge*. Stated differently, job characteristics should not be uniquely categorized as resource or demand.

### 2025-08-21 Submission.tex
avoiding conflict - stashing desktop and accepting these laptop revisions

Participants were first asked to think about whether or not their job could be described as consisting of these job characteristics. If a respondent indicated that any one characteristic was not applicable for their job (e.g., answered \emph{never} or \emph{not at all}), they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment). All questions were administered in randomized order within blocks of characteristic, resource, challenge, and hindrance.

@@

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/overallhist-1.pdf}
\caption{\label{fig:overallhist}Frequency distribution of standard deviations across characteristics deemed resources, challenges, and demands.}
\end{figure}

@@

H1 posits that the same job characteristic is not necessarily experienced similarly across workers - as hindrance, challenge, or resource. We explore this hypothesis first at the job characteristic level before presenting a broader perspective. Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present only extreme snapshots of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources. The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} Figure \ref{fig:combinegraphs} presents the resources, challenges, and hindrances that are \emph{most consistently agreed on} as indexed by lowest empirical standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers. The figures demonstrate that what is perceived as resource and challenge tends to be somewhat agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86). However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).

In addition to highlighting extremely agreed-- or disagreed--upon characteristics, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items. Here, discrepancies receive greater context, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram). Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to \emph{hindrances}, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01). In sum, these results provide some collective support for H1, and particularly so for hindrances, which are differently experienced across our raters.

The second hypothesis, similarly oriented to H1, stated that job characteristics would not be \emph{uniquely} categorized as a resource or demand. Table 1 provides the correlations among the O*NET ``scale''--level groupings\footnote{Survey items are grouped by O*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc). These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.} across evaluations as resource, challenge, and hindrance. Here would expect trivial correlations if job characteristics \emph{were} uniquely categorized. First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16). Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17. When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.

The mean resource to challenge correlations within the same dimension ranged from .62 to .66 (\emph{M} = .64, \emph{SD} = .02; for example, the association between information input ratings as a resource and as a challenge was .62). The correlations between resources and challenges \emph{across} dimensions (for example, the correlation between mental processes and work output was .42 and .39) ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12. The resource-hindrance correlations within the same dimension ranged from -.16 to -.30 (\emph{M} = -.24, \emph{SD} = .05), while the correlations between resources and hindrances \emph{across} dimensions ranged from .05 to -.27, \emph{M} = -.14, \emph{SD} = .08. The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27 (\emph{M} = -.21, \emph{SD} = .08). The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, \emph{M} = -.11, \emph{SD} = .09. In summary, correlations were larger when what was being rated was the same type of characteristic. Challenge and hindrance demands demonstrated smaller relationships, but mostly negative. Challenges and resources within the same O*NET dimensions are strongly and positively related. These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a \emph{resource} being also perceived as a \emph{challenge}. Stated differently, job characteristics should not be uniquely categorized as resource or demand.

@@

>>>>

Participants were first asked to think about whether or not their job could be described as consisting of these job characteristics. If a respondent indicated that any one characteristic was not applicable for their job (e.g., answered \emph{never} or \emph{not at all}), they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment). These ratings were made along a 5--point Likert--type agreement scale with values of (1) Strongly Disagree, (2) Disagree, (3) Neither Agree nor Disagree, (4) Agree, and (5) Strongly Agree. All questions were administered in randomized order within blocks of characteristic, resource, challenge, and hindrance.

@@

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/overallhist-1.pdf}
\caption{\label{fig:overallhist}Frequency distributions of standard deviations across characteristics rated as resources, challenges, and demands.}
\end{figure}

@@

H1 posits that \emph{not everyone agrees} that a characterisitic is a hindrance, challenge, or resource. Figure \ref{fig:overallhist} presents standard deviations of characteristic rating across all rated items. Here,the \emph{spread} of difference exhibits wider distributions of (dis)agreement for challenge and resource ratings (and a relatively more leptokurtic distribution of (dis)agreement for hindrances). The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to \emph{hindrances}, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01).

Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources. The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} Figure \ref{fig:combinegraphs} presents the \emph{most consistently agreed on} resources, hindrances, and challenges as indexed by lowest empirical standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers. The figures again highlight that what is perceived as resource and challenge tends to be relatively agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86). However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16). In sum, these results provide some collective support for H1, and particularly so for hindrances, which are differently experienced across our raters.

The second hypothesis, similarly oriented to H1, stated that job characteristics would not be \emph{uniquely} categorized as a resource or demand. We explore this via pattern of correlation similar to Campbell and Fiske (1959)'s multi--trait multi--method matrix. Table 1 provides the correlations among the O*NET ``scale''--level groupings\footnote{Survey items are grouped by O*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc). These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.} across evaluations as resource, challenge, and hindrance. Here would expect trivial correlations if job characteristics \emph{were} uniquely categorized. First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16). Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17. When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.

The mean resource to challenge correlations within the same dimension ranged from .62 to .66 (\emph{M} = .64, \emph{SD} = .02; for example, the association between information input ratings as a resource and as a challenge was .62). The correlations between resources and challenges \emph{across} dimensions (for example, the correlation between mental processes {[}resource{]} and work output {[}challenge{]} was .39) ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12. The resource-hindrance correlations within the same dimension ranged from -.16 to -.30 (\emph{M} = -.24, \emph{SD} = .05), while the correlations between resources and hindrances \emph{across} dimensions ranged from .05 to -.27, \emph{M} = -.14, \emph{SD} = .08. The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27 (\emph{M} = -.21, \emph{SD} = .08). The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, \emph{M} = -.11, \emph{SD} = .09. In summary, correlations were larger when what was being rated was the same type of characteristic. Challenge and hindrance demands demonstrated smaller relationships, but mostly negative. Challenges and resources within the same O*NET dimensions are strongly and positively related. These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a \emph{resource} being also perceived as a \emph{challenge}. Stated differently, job characteristics should not be uniquely categorized as resource or demand.

@@

\leavevmode\vadjust pre{\hypertarget{ref-campbell1959convergent}{}}%
Campbell DT and Fiske DW (1959) Convergent and discriminant validation by the multitrait-multimethod matrix. \emph{Psychological bulletin} 56(2). American Psychological Association: 81--105.
